\documentclass[a4paper]{scrartcl}

\usepackage{cv}

\author{Oscar Barlow}
\title{Oscar Barlow}
\cvsubtitle{hi@oscarbarlow.com | oscarbarlow.com/writing}
\date{}
\pagestyle{empty}

\begin{document}

\maketitle

\section*{Profile}
{ % Start of local scope
  \setlength{\parskip}{6pt plus 2pt minus 1pt}
  The pattern that runs through my career is convergence: turning a contested question with many
  plausible answers into one committed course, then building the structure so the decision keeps
  executing without me. I've shown this in retail competitive intelligence, banking data infrastructure,
  and AI governance under regulatory pressure. A second, related strength: translating frontier technology
  capabilities and risks into frameworks that let boards and teams move confidently, safely, and fast.
} % End of local scope

\section*{Advisory Expertise}
\begin{itemize}
  \item \textbf{Resolving contested calls:} When no one upstream has decided the direction and the
    direction is the hard part, I make the call, then build the team, architecture, and delegated
    ownership that keep it executing. The work is setting direction, not delegating a goal already set.
  \item \textbf{Turnaround under pressure:} Sometimes the problem is not too many options but a system
    already on fire. I enter broken, high-stakes systems and converge them on a working state.
  \item \textbf{Making technology legible:} I translate the capability and risk of AI into operating
    models that regulators and investors will scrutinise: proportionate guardrails that create value,
    not blanket caution. At Starling I prepared management's advocacy lines, later placed in the media
    and used in public and regulatory forums.
\end{itemize}

\section*{Career Highlights}

\subsection*{Head of AI Advocacy --- Starling Bank}
\textbf{January 2025--Present}

Built Starling's Responsible AI Innovation team and directed the governance overhaul of model risk
management. Its proportionate guardrails unlocked innovation within regulatory expectations and kept
working without me in every loop: a 40-person AI Champions network, 70\% daily staff AI usage, and three
customer-facing AI features shipped by others. Ran a board teach-in so the board could assess its own AI
risk exposure directly; speaker at the Banking Transformation Summit, FStech, Velocity, and the Cambridge
Judge Business School podcast.

\subsection*{Senior Engineering Manager, Data \& AI --- Starling Bank}
\textbf{November 2021--December 2024}

Resolved the contested direction for Starling's data platform, committing the organisation to Kafka
streaming and a cloud-native BigQuery/dbt warehouse. Scaled data engineering from 6 to 25, durable
capability that carried the direction forward, securing trusted data access for 300+ users (``Whenever
I want data, I've got it,'' noted the MRLO). Prevented £2M in annual fraud losses with re-engineered
model architecture; doubled ML deployment frequency.

\subsection*{Senior Consultant --- Infinity Works (Accenture)}
\textbf{June 2017--October 2021}

Directed the turnaround of a failing competitive intelligence platform at Sainsbury's, reaching
production launch within three months and unlocking six-figure gains. Led data platform strategy for a £10M cloud migration
programme, reporting directly to the CTO and committing the organisation to a single architecture.
Converged the Nectar loyalty relaunch integrations.

\section*{Education}
\begin{itemize}
  \item MSc International Marketing --- Birkbeck, University of London
  \item BA (Hons) Philosophy --- University of Nottingham
\end{itemize}

\end{document}
