\documentclass[a4paper]{scrartcl}

\usepackage{cv}

\author{Oscar Barlow}
\title{Oscar Barlow}
\cvsubtitle{Engineering leader --- AI \& data systems in regulated financial services}
\date{}
\pagestyle{empty}

\begin{document}

\maketitle

\section*{Profile}
{ % Start of local scope
  \setlength{\parskip}{6pt plus 2pt minus 1pt}
  I build the data and AI systems that regulated banks run on --- and the governance that lets them
  put AI into production with the regulator onside. At Starling Bank I've worked both sides of that
  problem: the streaming platform and ML systems underneath, and the model-risk and assurance frameworks
  on top that turned AI from a compliance worry into shipped product. I'm an engineer first, so I know
  what's buildable because I've built it. In a delivery team, that's senior judgement grounded in the
  work: I shape the architecture, pressure-test the plan, and raise the hard questions while they're
  still cheap to fix.
} % End of local scope

\section*{How I Help}
\begin{itemize}
  \item \textbf{Getting AI into production, safely:} the hard part is rarely the model --- it's the
    model-risk, assurance and live monitoring (fairness, uncertainty) that make it defensible enough to
    ship in a regulated business. I've built that path end to end.
  \item \textbf{Data foundations worth building on:} most AI problems are really data problems; I've built
    the streaming platforms and governed, cloud-native warehouses a bank can genuinely trust.
  \item \textbf{Models that stay reliable:} a model that works in a notebook and one that holds up against
    fraud for years are different problems --- I know the failure modes (drift, brittle features, stale
    refresh) and how to design them out.
  \item \textbf{Teams that outlast the engagement:} I build engineering organisations, not dependencies
    --- the hiring bars, tooling and rituals that keep delivery fast and safe long after I've gone.
\end{itemize}

\section*{Selected Experience}

\subsection*{Head of AI Advocacy --- Starling Bank}
\textbf{January 2025--Present}

Lead Starling's company-wide AI adoption and built its Responsible AI Innovation team from scratch.
Overhauled model-risk and governance so the bank could put AI into production under FCA expectations ---
work that helped ship three public-facing AI features and drove daily AI use across staff to 70\%. I
also speak externally on AI in banking, including at the Banking Transformation Summit and on the
Cambridge Judge Business School podcast.

\subsection*{Senior Engineering Manager, Data \& AI --- Starling Bank}
\textbf{November 2021--December 2024}

Built Starling's streaming data platform (Kafka) and cloud-native warehouse (BigQuery, dbt), giving the
whole business trusted, self-serve data. Re-engineered the fraud-model training architecture to prevent
£2M in annual losses, and doubled ML deployment frequency by rebuilding the MLOps tooling and guardrails.
Grew the data engineering organisation from 6 to 25.

\subsection*{Senior Consultant --- Infinity Works (Accenture)}
\textbf{June 2017--October 2021}

Built data and AI systems for clients across financial services and retail. Rescued a failing
competitive-intelligence platform at Sainsbury's, rebuilding the architecture to a production launch in
three months and unlocking six-figure gains. Delivered the data pipelines for a £10M cloud migration
(Snowflake), reporting directly to the CTO.

\section*{Education}
MSc International Marketing --- Birkbeck, University of London \\
BA (Hons) Philosophy --- University of Nottingham

\end{document}
