\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}

\title{Oscar Barlow}
\date{}

\begin{document}

\maketitle

\section*{Introduction}
I'm a Data Practice Lead covering ML Governance \& Ops at
\href{https://www.starlingbank.com/}{Starling Bank} in London. I design and
build systems and teams to solve business problems with data and ML.

\section*{Key Achievements}
\begin{itemize}
    \item Created an 'accessible ML' framework at Starling, increasing the
          amount of ML models produced by making ML workflow tooling usable by a broader
          community (data analysts as well as data scientists)
    \item Shipped a real-time data platform at Starling; multiplying the number
          of people who could accomplish work in the data warehouse by 10x. Business
          feedback, "whenever I want data, it's there"
    \item Launched an internal, algorithmic competitive intelligence tool for a
          UK national supermarket, driving price competitiveness and product range
          decisions
\end{itemize}

\section*{Technical Skills}
The languages I know and whose ecosystems I'm most familiar with are:
\begin{itemize}
    \item Python 3
    \item Terraform (HCL)
    \item Java
\end{itemize}

\section*{Experience}

\subsection*{Data Practice Lead - Starling Bank}
\textbf{June 2023 - Present}
\begin{itemize}
    \item Senior engineering role with a remit covering ML governance (ethics,
          explainability) and ops at Starling
    \item Implemented drift detection on ML models in production
    \item Created an 'accessible ML' framework to increase the amount of ML
          happening at Starling
    \item Launched ML explainability data science research project
    \item Shipped Starling's first entirely cloud-trained models
\end{itemize}

\subsection*{Tech Lead - Starling Bank}
\textbf{November 2021 - June 2023}
\begin{itemize}
    \item Led problem discovery, technology selection, design and
          implementation for a project to relaunch Starling's data systems.
    \item Shipped a streaming platform to export data to an analytics database
          with millisecond latency, without impacting source databases.
    \item Grew and upskilled data engineering team 4x (including managing
          external partners).
    \item Improved and increased data exploitation by creating a self-serve
          system for data analysts and scientists
\end{itemize}

\subsection*{Shared Parental Leave}
\textbf{March 2021 - November 2021}

\subsection*{Senior Consultant - Infinity Works}
\textbf{Document Search System, December 2020 - March 2021}
\begin{itemize}
    \item Part of a team building a pipeline and web app to make internal
          documents searchable
\end{itemize}

\textbf{Web Development, June 2020 - September 2020}
\begin{itemize}
    \item Short-term engagement on the Government's coronavirus financial
          relief system.
\end{itemize}

\textbf{Data Warehouse, November 2019 - May 2020}
\begin{itemize}
    \item Architected and built pipelines from on-premise databases into
          Snowflake, as part of a £10m 2-year programme to integrate the client's gaming
          platform with the game brands belonging to the business that had recently
          acquired them.
    \item Coached my team in agile, cloud platform engineering, clean coding,
          and invested heavily in remote working practices as one team member was based
          in Australia.
\end{itemize}

\textbf{Competitive Intelligence, January 2019 - November 2019}
\begin{itemize}
    \item Led a small team to launch an internal competitive intelligence tool
          for Sainsbury's, allowing purchasers to review how competitive their product
          lines are, and to negotiate more advantageous pricing with suppliers, based on
          recommendations from our algorithm.
    \item Introduced continuous integration and continuous deployment, coached
          team members to write tests, migrated from legacy to cloud-native architecture.
    \item Presented about this project to VelocityEU conference, Berlin 2019.
\end{itemize}

\textbf{Loyalty Scheme, June 2017 - December 2018}
\begin{itemize}
    \item Member of a small team that built, launched, and supported
          \href{https://nectar.sainsburys.co.uk}{Nectar}, a greenfield redevelopment of
          the well-known loyalty programme operated by Sainsbury's supermarkets in the
          UK.
    \item Designed and owned the pipelines to the data science sister project
          to Nectar, consuming outputs and providing inputs.
    \item Mentored three other Infinity Works employees, and helped two
          progress from junior to midweight developer.
\end{itemize}

\subsection*{Junior Developer - Makers Academy/HSBC}
\textbf{April 2017 - June 2017}
\begin{itemize}
    \item Two-month consultancy contract - delivered an MVP of an internal tool
          for reconciling employee data from different sources.
\end{itemize}

\subsection*{Freelance Filmmaker}
\textbf{May 2014 - September 2016}
\begin{itemize}
    \item Directed a short documentary about contemporary dance. Wrote an
          advert for Aberlour whisky. Assistant Directed an X-Men prequel short.
\end{itemize}

\subsection*{Marketing Manager - Various Companies}
\textbf{June 2009 - April 2014}
\begin{itemize}
    \item Strategically repositioned a small web agency prior to its
          acquisition.
    \item Managed schedule of digital content and web events across Europe for
          an enterprise software vendor.
    \item Relaunched a self-published software product for people with specific
          learning difficulties, for a small software reseller/publisher.
\end{itemize}

\section*{Education}

\subsection*{Makers Academy}
\textbf{November 2016 - February 2017}
\begin{itemize}
    \item Europe's leading 12-week intensive development bootcamp.
\end{itemize}

\subsection*{MSc International Marketing - Birkbeck, University of London}
\textbf{September 2012 - June 2014}
\begin{itemize}
    \item Part-time business masters degree, completed while working full time.
          Dissertation: brand development for tech(-enabled) startups. Grade:
          distinction.
\end{itemize}

\subsection*{BA (Hons) Philosophy - University of Nottingham}
\textbf{September 2005 - June 2008}
\begin{itemize}
    \item Broad degree in which I studied formal logic, ethics, and cultural
          theory.
\end{itemize}

\section*{Hobbies}
Right now I enjoy:
\begin{itemize}
    \item Learning German
    \item Yoga
    \item Hiking
\end{itemize}

\end{document}
